An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis

### 2021-08-13 analysis/preliminaryAnalysis.Rmd
d_coding and d_journals combined to d_all

---
title: "An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis"
author: "Maia & Tom"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

<br>
We have now completed data collection for the first phase of this project. The preregistered study protocol is available [here](https://osf.io/cz9g3/). Below we present a preliminary analysis of the phase one data.

There are three types of guidance:
* journal specific i.e., guidance written specifically for a particular journal and including in author-facing instructions/guidance documentation
* publisher i.e., guidance written for a group of journals that share the same publisher, for example "Cell STAR Methods"
* external i.e., academic papers or non-publisher reporting guidelines (usually present on EQUATOR)

@@

>>>>

---
title: "An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis"
author: "Analysis performed by: Maia Salholz-Hillel & Tom Hardwicke"
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

## Introduction
<br>
We have now completed data collection for the first phase of this project. We extracted author-facing statistical guidance provided by the top-15 journals (by Impact Factor) in each of 22 scientific disciplines (i.e., total N = 330 journals). The preregistered study protocol is available [here](https://osf.io/cz9g3/). Below we present a preliminary analysis of the phase one data and highlight some issues to discuss as a team.

## Method summary

> **Operational definition of statistical guidance**: any advice or instruction related to the appropriate selection, implementation, reporting, or interpretation of statistical analyses.

We recorded whether each journal:

* Provided any statistical guidance at all
* Had a dedicated statistical guidance section
* Referred to statistical guidance in external sources (e.g., reporting guidelines or articles)
* If any statistical guidance was provided by the journal, we coded (YES/NO) whether it mentioned each of 20 statistical topics (e.g., "p-values"), and extracted the verbatim text.

**Note:** When journals referred to guidance in external sources, we have recorded the names of the sources, but *we have currently not extracted guidance from those sources*. We return to this point in the *issues to address* section at the end of this document.

All data extraction was performed by a first coder (DS, MM, TB, MSH) and a second coder (TEH) with any coding differences resolved through discussion.

**Note** Some publishers provided statistical guidance that was shared across their portfolio of journals (specifically, 32 Nature journals, 12 Cell journals, and 2 Frontiers journals) . Publisher guidance was coded by two team members (as above), but is represented in our data and analysis for each individual journal the guidance applies to. For example, the Nature guidance is inherited by 32 journals so appears 32 times in the dataset.

## Results

@@

## Issues to address

* Pre-registration including general clinical trials advice
* Coding of external guidance
